\section{Classically Simulable Quantum Circuits}
%Maybe some introduction, short sentence on what classical simulability is.
\subsection{Clifford Circuits and Stabilizer Formalism}

Quantum circuits comprised of only quantum gates from the Clifford group are known as \textit{Clifford Circuits}.
This family of circuits are of considerable interest due to their classical simulability, that is,
circuits of this construction can be efficiently simulated on a classical computer with polynomial
effort via the Gottesman-Knill theorem. For this reason, Clifford gates do not form
a set of universal quantum gates, meaning a universal quantum computer cannot be constructed using a set
of Clifford gates. A set of universal quantum gates allows for any unitary operation to be approximated to
arbitrary accuracy by a quantum circuit, constructed using only the original set of gates. Clifford
circuits are also known as Stabilizer circuits.

\textit{Stabilizer Formalism}. An arbitrary, pure quantum state, $|\psi\rangle$ is \textit{stabilized} by
a unitary operator, $S$ if $|\psi\rangle$  is an eigenvector of $S$, with eigenvalue 1, satisfying:
\begin{equation}
    S|\psi\rangle = |\psi\rangle
\end{equation}
The key idea here is that the quantum state can be described in terms of the unitaries that stabilize it, instead of the state itself.
This is due to $|\psi\rangle$ being the unique state that is stabilized by $S$. \cite{PhysRevA.70.052328}
This can be seen from considering the Pauli matrices, and the unique states they stabilize. In the one-qubit case these are
the $+1$ eigenstates of the pauli matrices (omitting normalisation factors);
\begin{align}
     & X(|0\rangle + |1\rangle) = |0\rangle + |1\rangle   \\
     & Y(|0\rangle + i|1\rangle) = |0\rangle + i|1\rangle \\
     & Z|0\rangle = |0\rangle
\end{align}

If given a group or subgroup of unitaries, $\cal U$, the vector space, $V$, of $n$ qubit states is
stabilized by $\cal U$ if every element of $V$ is stable under action from every element of $\cal U$.
This description is more appealing, as we can exploit mathematical techniques from group theory to
describe quantum states and vector spaces. More precisely, the group $\cal U$ can be described using it's
generators. In general, a set of elements  $g_1, \dots, g_d$ of a group, $\cal G$, generate the group
if every element of $\cal G$ can be written as a product of elements from the set of generators,
$g_1, \dots, g_d$, such that ${\cal G} \coloneqq \langle g_1, \dots, g_d\rangle$. For example,
consider the group ${\cal U} \equiv \{ I, Z_1Z_2, Z_2Z_3, Z_1Z_3\}$. ${\cal U}$ can be compactly written
as ${\cal U} = \langle Z_1Z_2, Z_2Z_3 \rangle$, by recognising $(Z_1Z_2)^2 = I$ and
$Z_1Z_3 = (Z_1Z_2)(Z_2Z_3)$.

This allows for the description of a quantum state, and subsequently it's dynamics, in terms of the generators
of a stabilizer group. To see how the dynamics of a state are represented in terms of generators, consider
a stabilizer state under the action of an arbitrary unitary operator:
\begin{align}
    UM|\psi \rangle =  UMU^{\dagger}U|\psi\rangle
\end{align}
The state $|\psi \rangle$ is an eigenvector of $M$ if and only if, $U |\psi\rangle$ is an
eigenvector of $UMU^{\dagger}$. Thus, the application of an unitary operator transforms
$M \to UMU^{\dagger}$. Moreover, if the state $|\psi \rangle$ is stabilized by $M$, then the evolved
state $U|\psi\rangle$ will be stabilized by $UMU^{\dagger}$. If $M$ is an element of a stabilizer group
$\cal S$ such that $M_1, \dots, M_l$ generate $\cal S$, then $UM_1U^{\dagger}, \dots, UM_lU^{\dagger}$ must generate
$U{\cal S}U^{\dagger}$. This implies that to compute the dynamics of a stabilizer, only the transformation of
the generators needs to be considered \cite{fault-tolerantQC}. It is because of this,
Clifford circuits are able to be efficiently classically simulated via the Gottesman-Knill theorem.
\begin{theorem}[Gottesman-Knill Theorem \cite{knillGottesman}]

    Given an $n$ qubit state $|\psi \rangle$, the following statements are equivalent:
    \begin{itemize}
        \item $|\psi \rangle$ can be obtained from $|0 \rangle^{\otimes n}$ by CNOT, Hadamard and phase gates only.
        \item $|\psi \rangle$ is stabilized by exactly $2^n$ Pauli operators
        \item $|\psi \rangle$ can be uniquely identified by the group of Pauli operators that
              stabilize $|\psi \rangle$.
    \end{itemize}
    %possibility for discussion of bits
    % Could also extend to qudits
\end{theorem}

\subsection{Non-interacting Fermi Circuits}
\subsubsection{Fermionic Fock Space}
Another class of circuits that are classically simulable, are known as non-interacting or free fermi circuits.
These circuits are built from a fermionic Fock space formalism, where the basic units of information are local
fermionic modes (LFMs). Each mode can be occupied or unoccupied in the same fashion as qubits, where
a mode $j$ is associated with an occupation number, $n_j = 0$ (unoccupied mode) or $n_j = 1$ (occupied mode).
The state space of a many-fermion system is the fermionic Fock space, ${\cal F} = {\cal H}_0 + {\cal H}_1$,
where ${\cal H}_0$ and ${\cal H}_1$ correspond to subspaces of even and odd number of particles respectively.
The natural basis vectors for a Fock space of $m$ LFMs are Fock states $|n_0, \dots, n_{m-1}\rangle$,
where each element is the previously mentioned occupation number, $n_j$ at each site \cite{DeFelice2019}.
This system is similar to the qubit set-up as the Hilbert space for $m$ LFMs is identified with the Hilbert space
of $m$ qubits such that
\begin{align*}
    |n_1, \dots, n_{k-1}\rangle \equiv | n_0 \rangle \otimes | n_1 \rangle \otimes \dots \otimes | n_{m-1} \rangle, &  & n_j = 0,1
\end{align*}
where the RHS of the expression descibes a system of $m$ qubits. This allows a mapping of a qubit system (spin 1/2 system) onto
a fermionic system via a Jordan-Wigner Transformation, such that the representation and dynamics of a quantum
state are described using creation and annihilation operators from second quantization.
The creation operator, $a_j^{\dagger}$ creates a fermion at mode $j$ (if the mode is unoccupied),
whilst the annihilation operator, $a_j$ removes a fermion at site $j$ if the mode is occupied.
In the case of fermions, these operators obey canonical anti-commutation relations:
\begin{align}
    \{a_i, a_j\} \equiv \{a_i^{\dagger}, a_j^{\dagger}\} = 0 &  & \{a_i, a_j^{\dagger}\} = \delta_{ij}I
\end{align}
The occupation number, $n_j$ is then the eigenvalue of the number operator, $\hat{n}_j = a^{\dagger}_j a_j$
The creation and annihilation operators act on Fock states in the following way:
\begin{widetext}
    \begin{align*}
        a_j^{\dagger} |n_0, \dots, n_j, \dots, n_{m-1}\rangle = (-1)^{\sum^{j-1}_{s=0}n_s}\delta_{n_j, 1}  |n_0, \dots, n_j', \dots, n_{m-1}\rangle \\
        a_j |n_0, \dots, n_j, \dots, n_{m-1}\rangle = (-1)^{\sum^{j-1}_{s=0}n_s}\delta_{n_j, 0}  |n_0, \dots, n_j', \dots, n_{m-1}\rangle
    \end{align*}
\end{widetext}
Where $n_j'$ is the updated occupation number at the $j$th site.
To prepare an arbitrary Fock state, $|{\mathbf n}\rangle$, from a vacuum, $|{\mathbf 0}\rangle = |0,0,\dots,0\rangle$,
with fermions occupying arbitrary positions, creation operators are labeled to act on specified modes:

\begin{equation}
    |{\mathbf n}\rangle = a_{i_1}^{\dagger} a_{i_2}^{\dagger}\dots a_{i_m}^{\dagger}|{\mathbf 0}\rangle
\end{equation}

\subsubsection{Fermionic Circuits}
A fermionic circuit is constructed from a sequence of elementary gates that mediate an interaction between
modes $j$ and $k$, written as $U = e^{iH_g}$.$H_g$ is a general gate Hamiltonian:
\begin{equation}\label{gateham}
    H_g = b_{jj}a_j^{\dagger}a_j + b_{kk} a_{k}^{\dagger}a_{k} + b^{*}_{jk}a_k^{\dagger}a_j,
\end{equation}
where $b_{jj}, b_{jk}, b_{kk}$ are complex coefficients that form a hermitian matrix, $\mathbf b$.
The circuit is constructed by defining the
sequence of gates as $U = U_{\text{poly}(n)} \dots U_2 U_1$, such that the number of gates is no more than a
polynomial in order to be simulated classically. Then considering the evolution of Fock state in a circuit, given that the
circuit preserves the number of fermions ($U|{\mathbf 0}\rangle = |{\mathbf 0}\rangle  $), the state evolves as:
\begin{align}
    U a_j^{\dagger} |{\mathbf 0}\rangle = U a_j^{\dagger} U^{\dagger}U |{\mathbf 0}\rangle = U a_j^{\dagger} U^{\dagger} |{\mathbf 0}\rangle
\end{align}
Where $U$ acts by conjugation as
\begin{equation}
    U a_j^{\dagger} U^{\dagger} = \sum_s B_{is} a_s^{\dagger}
\end{equation}
and the matrix $B = \exp(i{\mathbf b})$ is defined from the previous coefficient matrix in Eq. (\refeq{gateham}).
To compute the final state of the system, only the matrix $B$ needs evaluation, which is classically simulable if $U$ contains
a polynomial number of gates \cite{Terhal2001}. More generally, if $U$ acts on an arbitrary Fock state, $|{\mathbf n}\rangle$, it's action
is written as:
\begin{align}
    U |{\mathbf n}\rangle & = U a_{i_1}^{\dagger} a_{i_2}^{\dagger}\dots a_{i_m}^{\dagger}|{\mathbf 0}\rangle                                                    \\
                          & = \sum_{j_1 \dots j_k} V_{i_1, j_1} \dots V_{i_k, j_k} a_{j_1}^{\dagger} a_{j_2}^{\dagger}\dots a_{j_k}^{\dagger}|{\mathbf 0}\rangle
\end{align}
Some simpler operators that act on Fock states, are the spin 1/2 Pauli operators, that are mapped onto a
non-interacting fermion system via the Jordan Wigner Transformation (JWT).
In particular, the set of Pauli operators that act on the $j$th mode,
$\{X_j, Y_j, Z_j\}$, can be expressed in terms of the creation and annihlation operators by first defining
the operators $\sigma^{\pm}_j = \frac{1}{2}(X_j \pm iY_j)$. Then in terms of the creation and annihilation
operators:
\begin{align}
    \sigma^{+}_j = e^{i\pi\sum^{j-1}_{m = 0} a^{\dagger}_m a_m} a_j^{\dagger} \\
    \sigma^{-}_j = e^{i\pi\sum^{j-1}_{m = 0} a^{\dagger}_m a_m} a_j
\end{align}















